### 2014-05-21 acks.tex
Add Emily, Silas, and Anne Hunter

My informal ``backup advisors'' on the ninth floor---Nickolai
Zeldovich and M.~Frans Kaashoek---have been patient through
innumerable practice talks and late-night idea-bouncing
sessions. Outside the ninth floor, I have been fortunate to have the
support and counsel of Victor Bahl, Hal Abelson, Jonathan Zittrain,
and Mike Walfish.

@@

To my labmates and ninth floor coinhabitants---Katrina LaCurts, Raluca
Ada Popa, Shuo Deng, Lenin Ravindranath, Ravi Netravali, Peter
Iannucci, Tiffany Chen, Amy Ousterhout, Jonathan Perry, Neha Narula,
Austin Clements, Cody Cutler, Eugene Wu, Dan Ports, and Sheila
Marian---thank you for your companionship and our time together.

>>>>

My informal ``backup advisors'' on the ninth floor---Nickolai
Zeldovich and M.~Frans Kaashoek---have been patient through
innumerable practice talks and late-night idea-bouncing
sessions. Outside the ninth floor, I have been fortunate to have the
support and counsel of Victor Bahl, Hal Abelson, Mike Walfish,
Jonathan Zittrain, and Anne Hunter.

@@

To my labmates and ninth floor coinhabitants---Katrina LaCurts, Raluca
Ada Popa, Shuo Deng, Lenin Ravindranath, Ravi Netravali, Peter
Iannucci, Tiffany Chen, Amy Ousterhout, Jonathan Perry, Neha Narula,
Austin Clements, Emily Stark, Cody Cutler, Eugene Wu, Dan Ports, Silas
Boyd-Wickizer, and Sheila Marian---thank you for your companionship
and our time together.
